### 2017-06-14 dark_knight/dark_knight.Rmd
Initial commit

---
title: "Analyzing scene direction from *The Dark Knight*"
author: "Julia Silge"
date: '`r Sys.Date()`'
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(cache = TRUE, warning = FALSE, message = FALSE, 
                      echo = FALSE, dpi = 360)
options(width=80, dplyr.width = 150)
library(ggplot2)
library(silgelib)
theme_set(theme_roboto())
```

```{r}
library(tidyverse)
library(tidytext)

scene_direction <- read_tsv("set-directions.txt", 
                            col_names = c("line", "text"))
```

```{r}
bigrams <- scene_direction %>%
    unnest_tokens(bigram, text, token = "ngrams", n = 2, collapse = FALSE)

bigrams_separated <- bigrams %>%
    separate(bigram, c("word1", "word2"), sep = " ")
```

```{r}
pronoun_bigrams <- bigrams_separated %>%
  filter(word1 %in% c("he", "she"))

pronoun_bigrams
```

```{r dark_knight, fig.width=7, fig.height=6}
pronoun_ratio <- pronoun_bigrams %>%
  count(word1, word2) %>%
  spread(word1, n, fill = 0) %>%
  mutate(total = he + she,
         he = (he + 1) / sum(he + 1),
         she = (she + 1) / sum(she + 1),
         logratio = log2(she / he)) %>%
  arrange(desc(logratio))

pronoun_ratio %>%
    filter(total > 2) %>%
    group_by(logratio < 0) %>%
    top_n(15, abs(logratio)) %>%
    ungroup() %>%
    mutate(word = reorder(word2, logratio)) %>%
    ggplot(aes(word, logratio, color = logratio < 0)) +
    geom_segment(aes(x = word, xend = word,
                     y = 0, yend = logratio), 
                 size = 1.1, alpha = 0.6) +
    geom_point(size = 3.5) +
    coord_flip() +
    labs(x = NULL, 
         y = "Relative appearance after 'she' compared to 'he'",
         title = "Words paired with 'he' and 'she' in The Dark Knight",
         subtitle = "Men pull, smile, slam, walk; women open, stand, see") +
    scale_color_discrete(name = "", labels = c("More 'she'", "More 'he'")) +
    scale_y_continuous(breaks = seq(-3, 3),
                       labels = c("0.125x", "0.25x", "0.5x", 
                                  "Same", "2x", "4x", "8x"))
```

### 2017-06-14 find_bigrams.Rmd
Initial commit

---
title: "Analyzing scene direction from whole sample of movies"
author: "Julia Silge"
date: '`r Sys.Date()`'
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(cache = TRUE, warning = FALSE, message = FALSE, 
                      echo = FALSE, dpi = 360)
options(width=80, dplyr.width = 150)
library(ggplot2)
library(silgelib)
theme_set(theme_roboto())
```

```{r pronoun_bigrams}
library(tidyverse)
library(tidytext)
library(stringr)

all_tsvs <- paste0("setDirections/", list.files(path = "setDirections/", pattern = ".tsv$"))

pronoun_bigrams <- all_tsvs %>%
    map_df(~data_frame(lines = read_lines(.)) %>%
    filter(str_detect(lines, "^[0-9]")) %>%
    separate(lines, c("line", "text"), sep = "\t") %>%
    unnest_tokens(bigram, text, token = "ngrams", 
                             n = 2, collapse = FALSE) %>%
               separate(bigram, c("word1", "word2"), sep = " ") %>%
               filter(word1 %in% c("he", "she")))

pronoun_bigrams
```

```{r pronoun_ratio, dependson="pronoun_bigrams", fig.width=7, fig.height=6}
pronoun_ratio <- pronoun_bigrams %>%
    count(word1, word2) %>%
    spread(word1, n, fill = 0) %>%
    mutate(total = he + she,
           he = (he + 1) / sum(he + 1),
           she = (she + 1) / sum(she + 1),
           logratio = log2(she / he)) %>%
    arrange(desc(logratio)) %>%
    filter(!(word2 %in% c("door", "ad", "r", "e", "he", "dead", 
                          "len", "queen", "lp", "room", "other", "two", "ar")))

pronoun_ratio %>%
    filter(total > 100) %>%
    group_by(logratio < 0) %>%
    top_n(15, abs(logratio)) %>%
    ungroup() %>%
    mutate(word = reorder(word2, logratio)) %>%
    ggplot(aes(word, logratio, color = logratio < 0)) +
    geom_segment(aes(x = word, xend = word,
                     y = 0, yend = logratio), 
                 size = 1.1, alpha = 0.6) +
    geom_point(size = 3.5) +
    coord_flip() +
    labs(x = NULL, 
         y = "Relative appearance after 'she' compared to 'he'",
         title = "Words paired with 'he' and 'she' in film set directions",
         subtitle = "From 3000+ films, verbs mentioned 100+ times") +
    scale_color_discrete(name = "", labels = c("More 'she'", "More 'he'")) +
    scale_y_continuous(breaks = seq(-3, 3),
                       labels = c("0.125x", "0.25x", "0.5x", 
                                  "Same", "2x", "4x", "8x"))

pronoun_ratio %>%
    filter(total > 10) %>%
    mutate(freq = 2 ^ logratio) %>%
    write_csv("~/Desktop/pronoun_word_ratios.csv")
```

### 2017-06-14 connect_year_writer.Rmd
Working on some JOINS

---
title: "Connecting scene direction to year and writer"
author: "Julia Silge"
date: '`r Sys.Date()`'
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(cache = TRUE, warning = FALSE, message = FALSE, 
                      echo = FALSE, dpi = 360)
options(width=80, dplyr.width = 150)
library(ggplot2)
library(silgelib)
theme_set(theme_roboto())
```

## Reading in the data

```{r pronoun_bigrams}
library(tidyverse)
library(tidytext)
library(stringr)

all_tsvs <- paste0("setDirections/", list.files(path = "setDirections/", pattern = ".tsv$"))

pronoun_bigrams <- all_tsvs %>%
    map_df(~data_frame(lines = read_lines(.x)) %>%
               filter(str_detect(lines, "^[0-9]")) %>%
               separate(lines, c("line", "text"), sep = "\t") %>%
               mutate(scriptID = as.integer(str_extract(.x, "[\\d]+"))) %>%
               unnest_tokens(bigram, text, token = "ngrams", 
                             n = 2, collapse = FALSE) %>%
               separate(bigram, c("word1", "word2"), sep = " ") %>%
               filter(word1 %in% c("he", "she"))) %>%
    select(scriptID, line, word1, word2)

pronoun_bigrams
```

## Joining the bigrams to other metadata about the scripts

```{r pronoun_imdb, dependson="pronoun_bigrams"}

mapping <- read_csv("full_mapping.csv") %>%
    rename(imdb = imdb_id)

gender <- read_csv("gender.csv") %>%
    filter(important == "1",
           gender != "NULL")

genre <- read_tsv("imdb-genre.tsv") %>%
    rename(imdb = imdb_id)

metadata <- read_tsv("imdb-meta-data-title.tsv") %>%
    select(imdb, year) ## could also get title here if we want later

pronoun_imdb <- pronoun_bigrams %>%
    left_join(mapping, by = c("scriptID" = "id")) 
```

What kind of joining can I do? Year, genre, gender of writers/etc

```{r, dependson="pronoun_imdb"}
pronoun_imdb %>%
    inner_join(metadata, by = "imdb") ## to get year

pronoun_imdb %>%
    inner_join(genre, by = "imdb") ## to get genre

pronoun_imdb %>%
    inner_join(gender, by = "imdb") ## to get gender of writers, etc

```

### 2017-06-18 connect_year_writer.Rmd
Modeling change by year

@@
 ```{r, dependson="pronoun_imdb"}
-pronoun_imdb %>%
-    inner_join(metadata, by = "imdb") ## to get year
 
@@
 ```
+
+## Change by year
+
+```{r words_by_year, dependson="pronoun_imdb"}
+words_by_year <- pronoun_imdb %>%
+    inner_join(metadata, by = "imdb") %>% ## to get year
+    filter(word1 == "she",
+           str_detect(word2, "[a-z]+"),
+           nchar(word2) > 2,
+           !is.na(year),
+           year > 1980) %>%
+    mutate(year = 5 * year %/% 5) %>%
+    add_count(year) %>%
+    rename(year_total = n) %>%
+    add_count(word2) %>%
+    rename(word_total = n) %>%
+    filter(word_total > 50) %>%
+    count(word2, year, year_total)
+
+slopes <- words_by_year %>%
+    nest(-word2) %>%
+    mutate(models = map(data, ~ glm(cbind(n, year_total) ~ year, ., 
+                                    family = "binomial"))) %>%
+    unnest(map(models, tidy)) %>%
+    filter(term == "year") %>%
+    arrange(estimate)
+```
+
+```{r contractions, dependson="words_by_year", fig.width=7, fig.height=5}
+words_by_year %>%
+    inner_join(slopes %>%
+                   top_n(10, estimate), 
+               by = "word2") %>%
+    ggplot(aes(year, n / year_total, color = word2)) +
+    geom_line(alpha = 0.8, size = 1.3) +
+    labs(x = NULL, y = "Word frequency",
+         title = "Words paired with 'she' in script set directions",
+         subtitle = "Many of the words increasing in frequency with time are negative contractions")
+```
+
+```{r increasing, dependson="words_by_year", fig.width=7, fig.height=5}
+words_by_year %>%
+    inner_join(slopes %>%
+                   filter(str_detect(word2, "^[^’]*$")) %>%
+                   top_n(10, estimate), 
+               by = "word2") %>%
+    ggplot(aes(year, n / year_total, color = word2)) +
+    geom_line(alpha = 0.8, size = 1.3) +
+    labs(x = NULL, y = "Word frequency",
+         title = "Words paired with 'she' in script set directions",
+         subtitle = "More recently, women are more likely to inspect, drift, steal, exhale,  breathe")
+```
+
+```{r decreasing, dependson="words_by_year", fig.width=7, fig.height=5}
+words_by_year %>%
+    inner_join(slopes %>%
+                   top_n(-10, estimate), 
+               by = "word2") %>%
+    ggplot(aes(year, n / year_total, color = word2)) +
+    geom_line(alpha = 0.8, size = 1.3) +
+    labs(x = NULL, y = "Word frequency",
+         title = "Words paired with 'she' in script set directions",
+         subtitle = "In the past, women were more likely to jab, snuggle, fling, whirl, shriek")
+```

### 2017-06-18 connect_year_writer.Rmd
Modeling! Words in the past vs. more recently

@@
            str_detect(word2, "[a-z]+"),
+           word2 != "look",
            nchar(word2) > 2,

### 2017-06-18 connect_year_writer.Rmd
Add some explanation of modeling

@@
 knitr::opts_chunk$set(cache = TRUE, warning = FALSE, message = FALSE, 
-                      echo = FALSE, dpi = 360)
+                      echo = TRUE, dpi = 360)
 options(width=80, dplyr.width = 150)
@@
 
+We can use logistic regression modeling to find the words paired with "she" that have changed the fastest with time, either in a positive or negative direction.
+
 ```{r words_by_year, dependson="pronoun_imdb"}
@@
 ```
+
+I'm picturing an interactive version of this chart where the user can switch from increasing to decreasing, hover over the lines to see how they are changing. Maybe decide how many to see?
+
+Let's check the words that change for "he", to compare. (This probably won't go into the final essay.)
+
+```{r words_by_year_he, dependson="pronoun_imdb"}
+words_by_year <- pronoun_imdb %>%
+    inner_join(metadata, by = "imdb") %>% ## to get year
+    filter(word1 == "he",
+           str_detect(word2, "[a-z]+"),
+           word2 != "look",
+           nchar(word2) > 2,
+           !is.na(year),
+           year > 1980) %>%
+    mutate(year = 5 * year %/% 5) %>%
+    add_count(year) %>%
+    rename(year_total = n) %>%
+    add_count(word2) %>%
+    rename(word_total = n) %>%
+    filter(word_total > 100) %>%
+    count(word2, year, year_total)
+
+slopes <- words_by_year %>%
+    nest(-word2) %>%
+    mutate(models = map(data, ~ glm(cbind(n, year_total) ~ year, ., 
+                                    family = "binomial"))) %>%
+    unnest(map(models, tidy)) %>%
+    filter(term == "year") %>%
+    arrange(estimate)
+
+# increasing for "he"
+slopes %>% 
+    top_n(10, estimate)
+
+# decreasing for "he"
+slopes %>% 
+    top_n(-10, estimate)
+```
+
+So the change in contractions looks like it is more about how set directions are changing as a whole, not a difference for how women are portrayed.
+For the final modeling by year, I'll plan to filter contractions out.
+
+Also, HA -- women are exhaling and men are inhaling.

### 2017-06-18 connect_year_writer.Rmd
Gender ratio from writers/directors/etc

@@
 
-What kind of joining can I do? Year, genre, gender of writers/etc
+## Differences by gender of writer
 
-```{r, dependson="pronoun_imdb"}
+We can use the odds ratio to find words coming after "she" that are more likely to be used by female writers/directors/etc and those more likely to be used by male writers/directors/etc.
+Movies can have both, can have multiple writers and so forth, but the following analysis accounts for that.
 
-pronoun_imdb %>%
-    inner_join(genre, by = "imdb") ## to get genre
+```{r gender_ratio, dependson="pronoun_imdb", fig.width=7, fig.height=6}
+gender_ratio <- pronoun_imdb %>%
+    inner_join(gender, by = "imdb") %>% ## to get gender of writers, etc
+    filter(word1 == "she",
+           str_detect(word2, "[a-z]+"),
+           nchar(word2) > 2) %>%
+    group_by(word2) %>%
+    mutate(total = n_distinct(scriptID)) %>%
+    ungroup %>%
+    count(gender, word2, total) %>%
+    spread(gender, n, fill = 0) %>%
+    mutate(female = (female + 1) / sum(female + 1),
+           male = (male + 1) / sum(male + 1),
+           ratio = female / male,
+           logratio = log2(ratio)) %>%
+    arrange(desc(logratio))
 
-pronoun_imdb %>%
-    inner_join(gender, by = "imdb") ## to get gender of writers, etc
+gender_ratio %>%
+    filter(total > 50) %>%
+    group_by(logratio < 0) %>%
+    top_n(15, abs(logratio)) %>%
+    ungroup() %>%
+    mutate(word = reorder(word2, logratio)) %>%
+    ggplot(aes(word, ratio - 1, color = logratio < 0)) +
+    geom_segment(aes(x = word, xend = word,
+                     y = 0, yend = ratio - 1), 
+                 size = 1.1, alpha = 0.6) +
+    geom_point(size = 3.5) +
+    coord_flip() +
+    labs(x = NULL, 
+         y = "Relative use by women / men",
+         title = "Words paired with 'she' from writers/directors/etc of different genders",
+         subtitle = "From 4000+ films, verbs mentioned 50+ times\nWomen are more likely to portray women who write, fling, remember, wander\nMen are more likely to portray women who respond, emerge, believe, react") +
+    scale_color_discrete(name = "", labels = c("More from women", "More from men")) +
+    scale_y_continuous(breaks = c(-0.6, -0.4, -0.2, 0, 0.2, 0.4, 0.6, 0.8),
+                       labels = c("-60%", "-40%", "-20%", "Same", "+20%", "+40%", "+60%", "+80%"))
+```
 
+What are some words after "she" that have about the same likelihood to come from writers/directors/etc who are men and women?
+
+```{r dependson="gender_ratio"}
+gender_ratio %>%
+    filter(total > 50) %>%
+    arrange(abs(logratio))
 ```
+
+Words like "still", "and", "drives", "tries", "brings", "listens"...
 

### 2017-06-23 connect_year_writer.Rmd
Round out some thoughts on viz ideas, analysis

@@
 
-pronoun_bigrams <- all_tsvs %>%
+all_lines <- all_tsvs %>%
     map_df(~data_frame(lines = read_lines(.x)) %>%
@@
                separate(lines, c("line", "text"), sep = "\t") %>%
-               mutate(scriptID = as.integer(str_extract(.x, "[\\d]+"))) %>%
+               mutate(scriptID = as.integer(str_extract(.x, "[\\d]+"))))
+
+pronoun_bigrams <- all_lines %>%
     unnest_tokens(bigram, text, token = "ngrams", 
@@
     separate(bigram, c("word1", "word2"), sep = " ") %>%
-               filter(word1 %in% c("he", "she"))) %>%
+    filter(word1 %in% c("he", "she")) %>%
     select(scriptID, line, word1, word2)
@@
 ```
+
+## Overall ratios
+
+```{r pronoun_ratio, dependson="pronoun_bigrams", fig.width=7, fig.height=6}
+pronoun_ratio <- pronoun_bigrams %>%
+    count(word1, word2) %>%
+    spread(word1, n, fill = 0) %>%
+    mutate(total = he + she,
+           he = (he + 1) / sum(he + 1),
+           she = (she + 1) / sum(she + 1),
+           logratio = log2(she / he)) %>%
+    arrange(desc(logratio)) %>%
+    filter(!(word2 %in% c("door", "ad", "r", "e", "he", "dead", 
+                          "len", "queen", "lp", "room", "other", "two", "ar")))
+
+pronoun_ratio %>%
+    filter(total > 100) %>%
+    group_by(logratio < 0) %>%
+    top_n(15, abs(logratio)) %>%
+    ungroup() %>%
+    mutate(word = reorder(word2, logratio)) %>%
+    ggplot(aes(word, logratio, color = logratio < 0)) +
+    geom_segment(aes(x = word, xend = word,
+                     y = 0, yend = logratio), 
+                 size = 1.1, alpha = 0.6) +
+    geom_point(size = 3.5) +
+    coord_flip() +
+    labs(x = NULL, 
+         y = "Relative appearance after 'she' compared to 'he'",
+         title = "Words paired with 'he' and 'she' in film set directions",
+         subtitle = "From 3000+ films, verbs mentioned 100+ times") +
+    scale_color_discrete(name = "", labels = c("More 'she'", "More 'he'")) +
+    scale_y_continuous(breaks = seq(-3, 3),
+                       labels = c("0.125x", "0.25x", "0.5x", 
+                                  "Same", "2x", "4x", "8x"))
+```
+
+Overall, we see that women are more likely to squeal, giggle and sob in these set directions, while men are more likely to shoot, kill, vault, and amble.
+With the particular filtering and cleaning used to make this plot, there are `r pronoun_ratio %>% filter(total > 100) %>% nrow()` words in the data set that we can measure a ratio for, from over 4 times for "squeals" on down.
+One option for a visualization would be something like [this](https://qz.com/836813/10000-words-ranked-according-to-trumpiness/) from Quartz.
+We could put all 800+ words into the visualization as circles, similar to that type of layout.
+We could label particularly interesting ones, as well as all the ones at the extremes.
+
+What types of words are equally likely to be paired with "he" and "she"?
+
+```{r dependson="pronoun_ratio"}
+pronoun_ratio %>%
+    filter(total > 100) %>%
+    arrange(abs(logratio))
+```
+
+Both men and women concentrate, prop things/themselves, finish, and "just" or "might" do something.
+
+Another interesting layer to add somehow would be some snippets of text to the visualization. For example, for "squeals", we can see some of the examples.
+
+```{r dependson="pronoun_ratio"}
+all_lines %>%
+    filter(str_detect(text, "She squeals")) %>%
+    distinct(scriptID, text) %>%
+    select(text) %>%
+    tail() %>%
+    kable()
+```
+
+Depending on the visual design, we could have *one* example text for each highlighted word perhaps, visible when the user hovers, or several that randomly switch?
+We could also include film title information there.
 
@@
 Words like "still", "and", "drives", "tries", "brings", "listens"...
+
+We could make another visualization in the same style as the first one, but I worry that users may be confused since they are communicating different information.
+Maybe they should visually look quite different, perhaps bars for this one if we do circles for the first one.
+We could choose to only show the extremes here.
 

### 2017-07-01 draft_post.Rmd
Start a DRAFT POST

---
title: "Women in Film"
author: "Julia Silge"
date: '`r Sys.Date()`'
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(cache = TRUE, warning = FALSE, message = FALSE, 
                      echo = FALSE, dpi = 360)
options(width=80, dplyr.width = 150)
library(ggplot2)
library(silgelib)
theme_set(theme_roboto())
```

How are women portrayed in film? It's a complicated question, and that question might make you think of a male protagonist's romantic interest, or someone in trouble who needs to be rescued, or maybe Wonder Woman.

One way to quantitatively measure how women are portrayed in film is to look at set directions in film scripts. Set directions, if you're not familiar with them, are the part of a script that are not dialogue. They describe actions and reactions, and communicate to the actors, producers, and director what story the script is working to tell.

```{r pronoun_bigrams}
library(tidyverse)
library(googlesheets)
library(tidytext)
library(stringr)

public_scripts <- gs_title("Public Script Sources")
script_sample <- public_scripts %>%
    gs_read("public_scripts")

all_tsvs <- paste0("setDirections/", list.files(path = "setDirections/", pattern = ".tsv$"))
select_tsvs <- sort(paste0("setDirections/setDirections-", script_sample$script_id, ".tsv"))

sample_tsvs <- intersect(all_tsvs, select_tsvs)

all_lines <- sample_tsvs %>%
    map_df(~data_frame(lines = read_lines(.x)) %>%
               filter(str_detect(lines, "^[0-9]")) %>%
               separate(lines, c("line", "text"), sep = "\t") %>%
               mutate(scriptID = as.integer(str_extract(.x, "[\\d]+"))))

pronoun_bigrams <- all_lines %>%
    unnest_tokens(bigram, text, token = "ngrams", 
                  n = 2, collapse = FALSE) %>%
    separate(bigram, c("word1", "word2"), sep = " ") %>%
    filter(word1 %in% c("he", "she")) %>%
    select(scriptID, line, word1, word2) %>%
    filter(!str_detect(word2, "’|'"))

pronoun_bigrams
```

*Really rough mock-up of general idea for main viz:*

```{r pronoun_ratio, dependson="pronoun_bigrams", fig.width=5, fig.height=10}
pronoun_ratio <- pronoun_bigrams %>%
    count(word1, word2) %>%
    spread(word1, n, fill = 0) %>%
    mutate(total = he + she,
           he = (he + 1) / sum(he + 1),
           she = (she + 1) / sum(she + 1),
           logratio = log2(she / he)) %>%
    arrange(desc(logratio)) %>%
    filter(nchar(word2) > 1,
           !(word2 %in% c("door", "ad", "he", "1s", "lp",
                          "car", "himself", "pans", "dead")))

library(ggbeeswarm)
pronoun_ratio %>%
    top_n(800, total) %>%
    mutate(blank = "blank",
           word = reorder(word2, logratio)) %>%
    ggplot(aes(blank, logratio, label = word2)) +
    geom_beeswarm(color = "midnightblue", alpha = 0.4) +
    geom_text(family = "RobotoCondensed-Regular", size = 2.5, 
              vjust = 1.2, hjust = 1.2,
              check_overlap = TRUE) +
    theme_void()

pronoun_ratio %>%
    top_n(800, total) %>%
    mutate(freq = 2 ^ logratio) %>%
    write_csv("~/Desktop/pronoun_word_ratios.csv")
```

*Label all the outlier points, choose interesting other points to label. For all labeled points, have example text for interactive hover. For non-labeled points, show word on hover.*

```{r dependson="pronoun_ratio"}
all_lines %>%
    filter(str_detect(text, "She squeals")) %>%
    distinct(scriptID, text) %>%
    select(text) %>%
    tail() %>%
    kable()
```

```{r pronoun_imdb, dependson="pronoun_bigrams"}

mapping <- read_csv("full_mapping.csv") %>%
    rename(imdb = imdb_id)

gender <- read_csv("gender.csv") %>%
    filter(important == "1",
           gender != "NULL")

genre <- read_tsv("imdb-genre.tsv") %>%
    rename(imdb = imdb_id)

metadata <- read_tsv("imdb-meta-data-title.tsv") %>%
    select(imdb, year) ## could also get title here if we want later

pronoun_imdb <- pronoun_bigrams %>%
    left_join(mapping, by = c("scriptID" = "id")) 
```

*Rough mockup for viz of writer/director viz*

```{r gender_ratio, dependson="pronoun_imdb", fig.width=8, fig.height=8}
library(viridis)

she_gender_ratio <- pronoun_imdb %>%
    inner_join(gender, by = "imdb") %>% ## to get gender of writers, etc
    filter(word1 == "she",
           str_detect(word2, "[a-z]+"),
           nchar(word2) > 2) %>%
    group_by(word2) %>%
    mutate(total = n_distinct(scriptID)) %>%
    ungroup %>%
    count(gender, word2, total) %>%
    spread(gender, n, fill = 0) %>%
    mutate(female = (female + 1) / sum(female + 1),
           male = (male + 1) / sum(male + 1),
           she_ratio = female / male,
           she_logratio = log2(she_ratio)) %>%
    arrange(desc(she_logratio))

he_gender_ratio <- pronoun_imdb %>%
    inner_join(gender, by = "imdb") %>% ## to get gender of writers, etc
    filter(word1 == "he",
           str_detect(word2, "[a-z]+"),
           nchar(word2) > 2) %>%
    group_by(word2) %>%
    mutate(total = n_distinct(scriptID)) %>%
    ungroup %>%
    count(gender, word2, total) %>%
    spread(gender, n, fill = 0) %>%
    mutate(female = (female + 1) / sum(female + 1),
           male = (male + 1) / sum(male + 1),
           he_ratio = female / male,
           he_logratio = log2(he_ratio)) %>%
    arrange(desc(he_logratio))

she_gender_ratio %>%
    select(word2, she_ratio, she_logratio, she_total = total) %>%
    left_join(he_gender_ratio %>%
                  select(word2, he_ratio, he_logratio, he_total = total)) %>%
    top_n(300, she_total) %>%
    ggplot(aes(she_logratio, he_logratio, label = word2,
               size = (she_total + he_total),
               color = she_ratio / he_ratio)) +
    annotate("text", x = 0.8, y = 0.8,
             label = "Male and female writers\ndescribing women",
             family = "RobotoCondensed-Regular") +
    annotate("text", x = -0.8, y = -0.8,
             label = "Male and female writers\ndescribing men",
             family = "RobotoCondensed-Regular") +
     annotate("text", x = 0.8, y = -0.8,
             label = "Female writers describing women\nMale writers decribing men",
             family = "RobotoCondensed-Regular") +
     annotate("text", x = -0.8, y = 0.8,
             label = "Female writers describing men\nMale writers decribing women",
             family = "RobotoCondensed-Regular") +
   geom_vline(xintercept = 0, color = "gray50", lty = 2, size = 1.5) +
    geom_hline(yintercept = 0, color = "gray50", lty = 2, size = 1.5) +
    geom_text(family = "RobotoCondensed-Regular", size = 3, 
              vjust = 1.2, hjust = 1.2,
              check_overlap = TRUE) +
    geom_point(alpha = 0.5) +
    theme_void() +
    scale_y_continuous(limits = c(-1.1, 1.1)) +
    scale_x_continuous(limits = c(-1.1, 1.1)) +
    scale_color_viridis(end = 0.8) +
    theme(legend.position="none")

```

*Hover for word for all points*

### 2017-07-01 draft_post.Rmd
Rough mock-ups of three main viz components

@@
 
-How are women portrayed in film?
-It's a complicated question, and that question might make you think of a male protagonist's romantic interest, or someone in trouble who needs to be rescued, or maybe Wonder Woman.
+How are women portrayed in film? It's complicated; the question might make you think of a male protagonist's romantic interest, someone in trouble who needs to be rescued, or maybe Wonder Woman.
 
-One way to quantitatively measure how women are portrayed in film is to look at set directions in film scripts.
+One way to quantitatively measure how women are portrayed in film is to look at scene directions in film scripts.
 Set directions, if you're not familiar with them, are the part of a script that are not dialogue.
@@
 
-```{r pronoun_bigrams}
+```{r pronoun_bigrams, echo=FALSE}
 library(tidyverse)
@@
 script_sample <- public_scripts %>%
-    gs_read("public_scripts")
+    gs_read("public_scripts", verbose = FALSE)
 
@@
     filter(!str_detect(word2, "’|'"))
-
-pronoun_bigrams
 ```
@@
 
-```{r pronoun_ratio, dependson="pronoun_bigrams", fig.width=5, fig.height=10}
+```{r pronoun_ratio, echo = FALSE, dependson="pronoun_bigrams", fig.width=5, fig.height=10}
 pronoun_ratio <- pronoun_bigrams %>%
@@
 
-```{r dependson="pronoun_ratio"}
+Example text snippets for "she squeals":
+
+```{r, echo = FALSE, dependson="pronoun_ratio"}
 all_lines %>%
@@
 
-```{r pronoun_imdb, dependson="pronoun_bigrams"}
+```{r pronoun_imdb, echo = FALSE, dependson="pronoun_bigrams"}
 
@@
 
+## Impact of producers, writers, and directors
+
 *Rough mockup for viz of writer/director viz*
 
-```{r gender_ratio, dependson="pronoun_imdb", fig.width=8, fig.height=8}
+```{r gender_ratio, echo = FALSE, dependson="pronoun_imdb", fig.width=8, fig.height=8}
 library(viridis)
@@
     annotate("text", x = 0.8, y = 0.8,
-             label = "Male and female writers\ndescribing women",
+             label = "Male and female creators\ndescribing women",
              family = "RobotoCondensed-Regular") +
     annotate("text", x = -0.8, y = -0.8,
-             label = "Male and female writers\ndescribing men",
+             label = "Male and female creators\ndescribing men",
              family = "RobotoCondensed-Regular") +
      annotate("text", x = 0.8, y = -0.8,
-             label = "Female writers describing women\nMale writers decribing men",
+             label = "Female creators describing women\nMale creators decribing men",
              family = "RobotoCondensed-Regular") +
      annotate("text", x = -0.8, y = 0.8,
-             label = "Female writers describing men\nMale writers decribing women",
+             label = "Female creators describing men\nMale creators decribing women",
              family = "RobotoCondensed-Regular") +
@@
 *Hover for word for all points*
+
+## Word use changing with time
+
+```{r changing_women, echo = FALSE, dependson="pronoun_imdb", fig.width=8, fig.height=6}
+library(ggrepel)
+words_by_year <- pronoun_imdb %>%
+    inner_join(metadata, by = "imdb") %>% ## to get year
+    filter(word1 == "she",
+           str_detect(word2, "[a-z]+"),
+           !(word2 %in% c("look", "doesn")),
+           nchar(word2) > 2,
+           !is.na(year),
+           year > 1980) %>%
+    mutate(year = 5 * year %/% 5) %>%
+    add_count(year) %>%
+    rename(year_total = n) %>%
+    add_count(word2) %>%
+    rename(word_total = n) %>%
+    filter(word_total > 50) %>%
+    count(word2, year, year_total)
+
+slopes <- words_by_year %>%
+    nest(-word2) %>%
+    mutate(models = map(data, ~ glm(cbind(n, year_total) ~ year, ., 
+                                    family = "binomial"))) %>%
+    unnest(map(models, tidy)) %>%
+    filter(term == "year") %>%
+    arrange(estimate)
+
+plot_words <- words_by_year %>%
+    inner_join(slopes %>%
+                   top_n(10, estimate), 
+               by = "word2") %>%
+    mutate(year = 10 * year %/% 10) %>%
+    filter(year %in% c(1980, 2010)) %>%
+    group_by(word2, year) %>%
+    summarise(n = sum(n),
+              total = sum(year_total)) %>%
+    mutate(Change = "Increasing") %>%
+    bind_rows(words_by_year %>%
+                  inner_join(slopes %>%
+                                 top_n(-10, estimate), 
+                             by = "word2") %>%
+                  mutate(year = 10 * year %/% 10) %>%
+                  filter(year %in% c(1980, 2010)) %>%
+                  group_by(word2, year) %>%
+                  summarise(n = sum(n),
+                            total = sum(year_total)) %>%
+                  mutate(Change = "Decreasing")) %>% 
+    ungroup
+
+ggplot(plot_words, aes(year, n / total, color = word2)) +
+    geom_line(size = 1.5, alpha = 0.5) +
+    geom_point(size = 4) +
+    geom_text_repel(data = subset(plot_words, year == 1980 & Change == "Decreasing"),
+                  aes(x = year, y = n / total, label = word2),
+                  color = "gray20", family = "RobotoCondensed-Regular",
+                  point.padding = unit(0.4, "lines")) +
+    geom_text_repel(data = subset(plot_words, year == 2010 & Change == "Increasing"),
+                  aes(x = year, y = n / total, label = word2),
+                  color = "gray20", family = "RobotoCondensed-Regular",
+                  point.padding = unit(0.4, "lines")) +
+    theme(legend.position="none") +
+    facet_wrap(~Change, ncol = 2) +
+    labs(x = NULL, y = "Word frequency",
+         title = "Words paired with 'she' in script set directions")
+```
+
+```{r changing_men, echo = FALSE, dependson="pronoun_imdb", fig.width=8, fig.height=6}
+library(ggrepel)
+words_by_year <- pronoun_imdb %>%
+    inner_join(metadata, by = "imdb") %>% ## to get year
+    filter(word1 == "he",
+           str_detect(word2, "[a-z]+"),
+           !(word2 %in% c("look", "doesn", "were", 
+                          "too", "see", "doing", "going")),
+           nchar(word2) > 2,
+           !is.na(year),
+           year > 1980) %>%
+    mutate(year = 5 * year %/% 5) %>%
+    add_count(year) %>%
+    rename(year_total = n) %>%
+    add_count(word2) %>%
+    rename(word_total = n) %>%
+    filter(word_total > 50) %>%
+    count(word2, year, year_total)
+
+slopes <- words_by_year %>%
+    nest(-word2) %>%
+    mutate(models = map(data, ~ glm(cbind(n, year_total) ~ year, ., 
+                                    family = "binomial"))) %>%
+    unnest(map(models, tidy)) %>%
+    filter(term == "year") %>%
+    arrange(estimate)
+
+plot_words <- words_by_year %>%
+    inner_join(slopes %>%
+                   top_n(10, estimate), 
+               by = "word2") %>%
+    mutate(year = 10 * year %/% 10) %>%
+    filter(year %in% c(1980, 2010)) %>%
+    group_by(word2, year) %>%
+    summarise(n = sum(n),
+              total = sum(year_total)) %>%
+    mutate(Change = "Increasing") %>%
+    bind_rows(words_by_year %>%
+                  inner_join(slopes %>%
+                                 top_n(-10, estimate), 
+                             by = "word2") %>%
+                  mutate(year = 10 * year %/% 10) %>%
+                  filter(year %in% c(1980, 2010)) %>%
+                  group_by(word2, year) %>%
+                  summarise(n = sum(n),
+                            total = sum(year_total)) %>%
+                  mutate(Change = "Decreasing")) %>% 
+    ungroup
+
+ggplot(plot_words, aes(year, n / total, color = word2)) +
+    geom_line(size = 1.5, alpha = 0.5) +
+    geom_point(size = 4) +
+    geom_text_repel(data = subset(plot_words, year == 1980 & Change == "Decreasing"),
+                  aes(x = year, y = n / total, label = word2),
+                  color = "gray20", family = "RobotoCondensed-Regular",
+                  point.padding = unit(0.4, "lines")) +
+    geom_text_repel(data = subset(plot_words, year == 2010 & Change == "Increasing"),
+                  aes(x = year, y = n / total, label = word2),
+                  color = "gray20", family = "RobotoCondensed-Regular",
+                  point.padding = unit(0.4, "lines")) +
+    theme(legend.position="none") +
+    facet_wrap(~Change, ncol = 2) +
+    labs(x = NULL, y = "Word frequency",
+         title = "Words paired with 'he' in script set directions")
+```
+
+*interactively switch from men to women, increasing to decreasing*

### 2017-07-01 draft_post.Rmd
Little bit of intro

@@
 One way to quantitatively measure how women are portrayed in film is to look at scene directions in film scripts.
-Set directions, if you're not familiar with them, are the part of a script that are not dialogue.
-They describe actions and reactions, and communicate to the actors, producers, and director what story the script is working to tell.
+Scene directions are the part of a script that are not dialogue, describing what's happening on screen and telling actors how to move and how to deliver their lines.
+These scene directions communicate to the actors, producers, and director what story the script is working to tell.
 

### 2017-07-16 draft_post.Rmd
Work on draft post

@@
 These scene directions communicate to the actors, producers, and director what story the script is working to tell.
+
+In this analysis, we found words that were paired with the pronouns "he" and "she" in these scene directions, then analyzed which words were more likely to come after one compared to the other.
+Which words are more likely to be used with "she" in film script scene directions compared to those used with "he"?
+Let's look at the top 800 words.
 
@@
 ## Impact of producers, writers, and directors
+
+Hollywood can be a tough place to work as a creative woman, writing, directing, or producing films.
+We can use our text mining approach to explore the impact that the gender of a creator has on how characters are portrayed.
+We used IMDB biographies, pictures, and names to manually classify the genders of writers, directors, and producers for our film script dataset.
+
+Gender can be a complicated identification for people, but English just has two singular third person pronouns traditionally used for people, "he" and "she".
+In this analysis, for both the text data and the identification of gender for film creators, we have chosen to identify men and women with the pronouns "he" and "she".
+Using this type of classification, a transgender woman (either a writer/director/producer or a character in a script) described with the pronoun "she" would be classified as a woman.
+
+Using these connections to who had a hand in creating
 

### 2017-07-16 draft_post.Rmd
Working on just writers

--- 2017-07-01 draft_post.Rmd
@@
     filter(important == "1",
-           gender != "NULL")
+           gender != "NULL",
+           role == "writer")
 
@@
 
-## Impact of producers, writers, and directors
+## Impact of writers
 
-*Rough mockup for viz of writer/director viz*
+*Rough mockup for viz of writer viz*
 
@@
 she_gender_ratio <- pronoun_imdb %>%
-    inner_join(gender, by = "imdb") %>% ## to get gender of writers, etc
+    inner_join(gender, by = "imdb") %>% ## to get gender of writers
     filter(word1 == "she",
@@
     annotate("text", x = 0.8, y = 0.8,
-             label = "Male and female creators\ndescribing women",
+             label = "Male and female writers\ndescribing women",
              family = "RobotoCondensed-Regular") +
     annotate("text", x = -0.8, y = -0.8,
-             label = "Male and female creators\ndescribing men",
+             label = "Male and female writers\ndescribing men",
              family = "RobotoCondensed-Regular") +
      annotate("text", x = 0.8, y = -0.8,
-             label = "Female creators describing women\nMale creators decribing men",
+             label = "Female writers describing women\nMale writers decribing men",
              family = "RobotoCondensed-Regular") +
      annotate("text", x = -0.8, y = 0.8,
-             label = "Female creators describing men\nMale creators decribing women",
+             label = "Female writers describing men\nMale writers decribing women",
              family = "RobotoCondensed-Regular") +
@@
 *Hover for word for all points*
+
+Add bar plot for just how women are portrayed
 

### 2017-07-16 draft_post.Rmd
Getting a nice draft ready

@@
 
-How are women portrayed in film? It's complicated; the question might make you think of a male protagonist's romantic interest, someone in trouble who needs to be rescued, or maybe Wonder Woman.
+How are women portrayed in film? It's complicated; that question might make you think of a male protagonist's romantic interest, a damsel in distress who needs to be rescued, or maybe Wonder Woman.
 
@@
 These scene directions communicate to the actors, producers, and director what story the script is working to tell.
+
+In this analysis, we used text mining to identify words that are paired with the pronouns "he" and "she" in scene directions for over 2000 film scripts for movies released from the 1930s to today.
+We then analyzed which words are more likely to come after one compared to the other.
+Which words are most likely to be used with "she" in film script scene directions compared to those used with "he"?
 
@@
 public_scripts <- gs_title("Public Script Sources")
-script_sample <- public_scripts %>%
+raw_script_sample <- public_scripts %>%
     gs_read("public_scripts", verbose = FALSE)
+
+new_ids <- read_csv("missing_scripts.csv")
+
+script_sample <- raw_script_sample %>% 
+    left_join(new_ids, by = c("script_id" = "missing_script_id",
+                                            "imdb_id")) %>%
+    mutate(script_id = ifelse(is.na(different_script_id), script_id, different_script_id))
 
@@
 
-*Really rough mock-up of general idea for main viz:*
-
-```{r pronoun_ratio, echo = FALSE, dependson="pronoun_bigrams", fig.width=5, fig.height=10}
+```{r pronoun_ratio, echo = FALSE, dependson="pronoun_bigrams", fig.width=8, fig.height=8}
 pronoun_ratio <- pronoun_bigrams %>%
@@
            !(word2 %in% c("door", "ad", "he", "1s", "lp",
-                          "car", "himself", "pans", "dead")))
+                          "car", "himself", "pans", "dead", 
+                          "queen", "back", "too", "were")))
 
+pronoun_ratio %>%
+    top_n(800, total) %>%
+    group_by(logratio < 0) %>%
+    top_n(15, abs(logratio)) %>%
+    ungroup() %>%
+    mutate(word = reorder(word2, logratio)) %>%
+    ggplot(aes(word, logratio, color = logratio < 0)) +
+    geom_segment(aes(x = word, xend = word,
+                     y = 0, yend = logratio), 
+                 size = 1.1, alpha = 0.6) +
+    geom_point(size = 3.5) +
+    coord_flip() +
+    labs(x = NULL, 
+         y = "Relative appearance after 'she' compared to 'he'",
+         title = "Words paired with 'he' and 'she' in film set directions",
+         subtitle = "From ~2000 films, of the top 800 words") +
+    scale_color_discrete(name = "", labels = c("More 'she'", "More 'he'")) +
+    scale_y_continuous(breaks = seq(-3, 3),
+                       labels = c("0.125x", "0.25x", "0.5x", 
+                                  "Same", "2x", "4x", "8x"))
+
+```
+
+There are dramatic differences in the kinds of words we see here.
+In movies, women are more likely to snuggle, giggle, squeal, and sob while men are more likely to gallop, shoot, howl, and kill.
+We see evidence here of the tropes and storytelling conventions that propel so many films, and how men, women, and their relationships are often portrayed.
+
+Now let's look at the top 800 words, including those that are used about evenly after "he" and "she".
+
+*Really rough mock-up of general idea for main viz:*
+
+```{r pronoun_circles, echo = FALSE, dependson="pronoun_ratio", fig.width=5, fig.height=10}
 library(ggbeeswarm)
@@
     mutate(freq = 2 ^ logratio) %>%
-    write_csv("~/Desktop/pronoun_word_ratios.csv")
+    write_csv("pronoun_word_ratios.csv")
 ```
@@
 
+Hollywood can be a tough place to work as a creative woman, either writing, directing, or producing films.
+We can use our text mining approach to explore the impact that the gender of a writer has on how characters are portrayed.
+We used IMDB biographies, pictures, and names to manually classify the genders of writers for our film script dataset.
+
+Gender can be a complicated identification for people, but English has two singular third person pronouns most often used for people, "he" and "she".
+In this analysis, for both the text data and the identification of gender for film writers, we have chosen to identify men and women with the pronouns "he" and "she".
+Using this type of classification, a transgender woman (either a writer or a character in a script) described with the pronoun "she" would be classified as a woman.
+
+Using this connection to who wrote these scripts, we can examine how writers who are men and women are portraying women in film.
+Do women writers portray women differently?
+How would the overall cultural representation of women be different if there were more women writing the movies we watch?
+
 ```{r gender_ratio, echo = FALSE, dependson="pronoun_imdb", fig.width=8, fig.height=8}
@@
 she_gender_ratio %>%
-    select(word2, she_ratio, she_logratio, she_total = total) %>%
+    top_n(300, total) %>%
+    group_by(she_logratio < 0) %>%
+    top_n(15, abs(she_logratio)) %>%
+    ungroup() %>%
+    mutate(word = reorder(word2, she_logratio)) %>%
+    ggplot(aes(word, she_logratio, color = she_logratio < 0)) +
+    geom_segment(aes(x = word, xend = word,
+                     y = 0, yend = she_logratio), 
+                 size = 1.1, alpha = 0.6) +
+    geom_point(size = 3.5) +
+    coord_flip() +
+    labs(x = NULL, 
+         y = "Relative use by writers who are women compared to men",
+         title = "Words used for women characters by women and men writers in film set directions",
+         subtitle = "From ~2000 films, of the top 300 words") +
+    scale_color_discrete(name = "", labels = c("More from women", "More from men")) +
+    scale_y_continuous(breaks = seq(-3, 3),
+                       labels = c("0.125x", "0.25x", "0.5x", 
+                                  "Same", "2x", "4x", "8x"))
+
+```
+
+In our dataset, about 15% of film writers are women and about 85% are men.
+If women were more equitably represented in the ranks of Hollywood writers, our analysis indicates we would see fewer women in movies disappearing, reacting, and sobbing and more women loving, writing, and searching.
+And flinging things around, apparently!
+
+This plot shows one way to look at differences between writers who are men and women.
+Let's look a little deeper, though, to learn more.
+For example, do some of these differences hold true no matter what kind of character a women is writing?
+What is the interaction between writers who are men and women and charactes who are men and women?
+
+```{r gender_scatter, echo = FALSE, dependson="gender_ratio", fig.width=8, fig.height=8}
+writer_ratios <- she_gender_ratio %>%
+    select(word2, she_freq = she_ratio, she_logratio, she_total = total) %>%
     left_join(he_gender_ratio %>%
-                  select(word2, he_ratio, he_logratio, he_total = total)) %>%
-    top_n(300, she_total) %>%
+                  select(word2, he_freq = he_ratio, he_logratio, he_total = total)) %>%
+    top_n(300, she_total)
+
+write_csv(writer_ratios, "./writer_ratios.csv")
+
+writer_ratios %>%
     ggplot(aes(she_logratio, he_logratio, label = word2,
                size = (she_total + he_total),
-               color = she_ratio / he_ratio)) +
-    annotate("text", x = 0.8, y = 0.8,
-             label = "Male and female writers\ndescribing women",
+               color = she_freq / he_freq)) +
+    annotate("text", x = 1.2, y = 1.2,
+             label = "Female writers\ndescribing men and women",
              family = "RobotoCondensed-Regular") +
-    annotate("text", x = -0.8, y = -0.8,
-             label = "Male and female writers\ndescribing men",
+    annotate("text", x = -1.2, y = -1.2,
+             label = "Male writers\ndescribing men and women",
              family = "RobotoCondensed-Regular") +
-     annotate("text", x = 0.8, y = -0.8,
+    annotate("text", x = 1.2, y = -1.2,
              label = "Female writers describing women\nMale writers decribing men",
              family = "RobotoCondensed-Regular") +
-     annotate("text", x = -0.8, y = 0.8,
+    annotate("text", x = -1.2, y = 1.2,
              label = "Female writers describing men\nMale writers decribing women",
@@
     theme_void() +
-    scale_y_continuous(limits = c(-1.1, 1.1)) +
-    scale_x_continuous(limits = c(-1.1, 1.1)) +
+    scale_y_continuous(limits = c(-1.6, 1.6)) +
+    scale_x_continuous(limits = c(-1.6, 1.6)) +
     scale_color_viridis(end = 0.8) +
     theme(legend.position="none")
-
 ```
@@
 
-Add bar plot for just how women are portrayed
+The size of the circle in this plot shows how often that word is used overall in film scripts; a word like "smiles" is used more often and a word like "understands" is used less often.
+Words close to an axis are used about the same with "he" and "she" for that kind of writer, and words far away from an axis exhibit more dramatic differences.
 
-## Word use changing with time
+There are some words that writers who are men and women are more likely to use, no matter what kind of character they are writing.
+In the upper right quadrant, we find the words that writers who are women are more likely to use.
+Writers who are women are more likely to write characters who sing, love, shift, sink into things, and burst into places.
+And lots of flinging!
+The lower left quadrant shows the words that writers who are men are more likely to use, for both male and female characters.
+Writers who are men are more likely to write characters who react, clutch, dive, shout, and emerge from places.
 
-```{r changing_women, echo = FALSE, dependson="pronoun_imdb", fig.width=8, fig.height=6}
+In the other quadrants, we can see remarkable differences in how writers who are men and women portray characters who are men and women.
+If you look in the upper left quadrant, we find words that writers use in describing characters of the opposite gender.
+There are some romantic and sexual words here, like "kiss", "gaze", and "stroke", as well as words that imply, well, less happy outcomes, such as "disappears" and "died".
+The lower right quadrant shows us the words that writers use to portray characters the same gender as them.
+These characters wince, jerk, fumble, and perhaps most remarkably, write on screen.
+There are verbs here that are active but less explicitly testosterone-fueled than the lower left quadrant; writers of the same gender create characters who crawl, climb, play, and scan.
+These characters also hear and understand.
+A woman in a movie doing such things is a far cry from the giggling, squealing, blushing character we met at the beginning of this essay.
+
+```{r changing_women, eval = FALSE, echo = FALSE, dependson="pronoun_imdb", fig.width=8, fig.height=6}
+## word use changing with time
+
 library(ggrepel)
@@
          title = "Words paired with 'she' in script set directions")
-```
 
-```{r changing_men, echo = FALSE, dependson="pronoun_imdb", fig.width=8, fig.height=6}
-library(ggrepel)
 words_by_year <- pronoun_imdb %>%
@@
 ```
-
-*interactively switch from men to women, increasing to decreasing*

### 2017-07-16 draft_post.Rmd
A little more cleaning

@@
     arrange(desc(logratio)) %>%
-    filter(nchar(word2) > 1,
+    filter(nchar(word2) > 2,
            !(word2 %in% c("door", "ad", "he", "1s", "lp",
                           "car", "himself", "pans", "dead", 
-                          "queen", "back", "too", "were")))
+                          "queen", "back", "too", "were",
+                          "doesn", "half")))
 
@@
 
-Example text snippets for "she squeals":
+```{r, echo = FALSE, dependson="pronoun_ratio"}
+example_text <- pronoun_ratio %>% 
+    top_n(800, total) %>% 
+    head(20) %>% 
+    select(word = word2) %>%
+    bind_rows(data_frame(word = c("cleans", "moans", "laughs", "twirls",
+                                  "lingers", "bursts", "retreats", "answer",
+                                  "creeps"))) %>%
+    bind_rows(pronoun_ratio %>% 
+                  top_n(800, total) %>% 
+                  tail(20) %>% 
+                  select(word = word2))
 
-```{r, echo = FALSE, dependson="pronoun_ratio"}
-all_lines %>%
-    filter(str_detect(text, "She squeals")) %>%
-    distinct(scriptID, text) %>%
-    select(text) %>%
-    tail() %>%
-    kable()
+example_text
 ```
@@
 For example, do some of these differences hold true no matter what kind of character a women is writing?
-What is the interaction between writers who are men and women and charactes who are men and women?
+What is the interaction between *writers* who are men and women and *characters* who are men and women?
 

### 2017-07-17 draft_post.Rmd
Cleaning, cleaning, and more cleaning

@@
                           "queen", "back", "too", "were",
-                          "doesn", "half")))
+                          "doesn", "half", "with", "been", 
+                          "who", "she", "the")))
 
@@
 ```{r, echo = FALSE, dependson="pronoun_ratio"}
-example_text <- pronoun_ratio %>% 
+example_words <- pronoun_ratio %>% 
     top_n(800, total) %>% 
@@
                                   "lingers", "bursts", "retreats", "answer",
-                                  "creeps"))) %>%
+                                  "creeps", "types", "attacks", "inhales",
+                                  "stares", "grimaces", "suddenly", "stops",
+                                  "ducks", "waits", "stomps", "remembers",
+                                  "scrambles", "splashes", "jerks", "throws",
+                                  "knows", "exhales", "coughs", "flops",
+                                  "crouches", "staggers", "forgets", "slashes"))) %>%
     bind_rows(pronoun_ratio %>% 
@@
 
-example_text
+pronouns <- c(sample(c("she", "She"), size = 36, replace = TRUE), 
+              sample(c("he", "He"), size = 36, replace = TRUE))
+
+example_text <- example_words %>%
+    mutate(pronoun = pronouns,
+           phrase = str_c(pronoun, word, sep = " ")) %>%
+    pull(phrase) %>%
+    map_df(function(x) all_lines %>%
+               filter(str_detect(text, x)) %>%
+               sample_n(1) %>%
+               select(text)) %>%
+    bind_cols(example_words) %>%
+    select(word, text)
+
+write_csv(example_text, "./example_texts.csv")
 ```

### 2017-07-17 draft_post.Rmd
Mmmmmmm, MOAR CLEANING

--- 2017-07-16 draft_post.Rmd
@@
                           "queen", "back", "too", "were",
-                          "doesn", "half")))
+                          "doesn", "half", "with", "been", 
+                          "who", "she", "the", "very",
+                          "and", "didn")))
 
@@
 There are dramatic differences in the kinds of words we see here.
-In movies, women are more likely to snuggle, giggle, squeal, and sob while men are more likely to gallop, shoot, howl, and kill.
+In movies, women are more likely to snuggle, giggle, squeal, and sob while men are more likely to strap things on, gallop, shoot, howl, and kill.
 We see evidence here of the tropes and storytelling conventions that propel so many films, and how men, women, and their relationships are often portrayed.
@@
     bind_rows(data_frame(word = c("cleans", "moans", "laughs", "twirls",
-                                  "lingers", "bursts", "retreats", "answer",
-                                  "creeps"))) %>%
+                                  "lingers", "bursts", "retreats", "answers",
+                                  "creeps", "types", "attacks", "inhales",
+                                  "stares", "grimaces", "suddenly", "stops",
+                                  "ducks", "waits", "stomps", "remembers",
+                                  "scrambles", "splashes", "jerks", "throws",
+                                  "knows", "exhales", "coughs", "flops",
+                                  "crouches", "staggers", "forgets", "slashes"))) %>%
     bind_rows(pronoun_ratio %>% 
@@
 
-example_text
+pronouns <- c(sample(c(" she", "She"), size = 36, replace = TRUE), 
+              sample(c(" he", "He"), size = 36, replace = TRUE))
+
+example_text <- example_words %>%
+    mutate(pronoun = pronouns,
+           phrase = str_c(pronoun, word, sep = " ")) %>%
+    pull(phrase) %>%
+    map_df(function(x) all_lines %>%
+               filter(str_detect(text, x)) %>%
+               sample_n(1) %>%
+               select(text)) %>%
+    bind_cols(example_words) %>%
+    select(word, text)
+
+write_csv(example_text, "./example_texts.csv")
 ```
@@
 The lower left quadrant shows the words that writers who are men are more likely to use, for both male and female characters.
-Writers who are men are more likely to write characters who react, clutch, dive, shout, and emerge from places.
+Writers who are men are more likely to write characters who react, clutch, dive, shout, ducks, and emerge from places.
 

### 2017-07-17 draft_post.Rmd
Working on some example texts

@@
     map_df(function(x) all_lines %>%
-               filter(str_detect(text, x)) %>%
+               filter(nchar(text) < 140,
+                      str_detect(text, x)) %>%
                sample_n(1) %>%
@@
 In the upper right quadrant, we find the words that writers who are women are more likely to use.
-Writers who are women are more likely to write characters who sing, love, shift, sink into things, and burst into places.
+Writers who are women are more likely to write characters who sing, love, shift, sink into things, and burst out or into places.
 And lots of flinging!

### 2017-07-17 draft_post.Rmd
Edit text a bit

@@
     map_df(function(x) all_lines %>%
-               filter(nchar(text) < 140,
+               filter(nchar(text) < 180,
                       str_detect(text, x)) %>%

### 2017-07-17 draft_post.Rmd
Minor tweaks to text

@@
 Let's look a little deeper, though, to learn more.
-For example, do some of these differences hold true no matter what kind of character a women is writing?
+For example, do some of these differences hold true no matter what kind of character a woman is writing?
 What is the interaction between *writers* who are men and women and *characters* who are men and women?
@@
 The lower left quadrant shows the words that writers who are men are more likely to use, for both male and female characters.
-Writers who are men are more likely to write characters who react, clutch, dive, shout, ducks, and emerge from places.
+Writers who are men are more likely to write characters who react, clutch, dive, shout, duck, and emerge from places.
 

### 2017-08-16 draft_post.Rmd
Updates based on feedback, work on viz

@@
 
+stop_words_vector <- stop_words %>% 
+                 filter(lexicon == "snowball") %>% 
+                 pull(word)
+
 pronoun_bigrams <- all_lines %>%
@@
     select(scriptID, line, word1, word2) %>%
-    filter(!str_detect(word2, "’|'"))
+    filter(!str_detect(word2, "’|'"),
+           nchar(word2) > 2,
+           !(word2 %in% c("door", "ad", "he", "1s", "lp",
+                          "car", "himself", "pans", "dead", 
+                          "queen", "back", "too", "were",
+                          "doesn", "half", "with", "been", 
+                          "who", "she", "the", "very",
+                          "and", "didn")),
+           !(word2 %in% stop_words_vector))
 ```
@@
            logratio = log2(she / he)) %>%
-    arrange(desc(logratio)) %>%
-    filter(nchar(word2) > 2,
-           !(word2 %in% c("door", "ad", "he", "1s", "lp",
-                          "car", "himself", "pans", "dead", 
-                          "queen", "back", "too", "were",
-                          "doesn", "half", "with", "been", 
-                          "who", "she", "the", "very",
-                          "and", "didn")))
+    arrange(desc(logratio))
 
@@
                   tail(20) %>% 
-                  select(word = word2))
+                  select(word = word2)) %>%
+    pull(word) %>% 
+    map(rep, 20) %>% 
+    flatten_chr()
 
-pronouns <- c(sample(c(" she", "She"), size = 36, replace = TRUE), 
-              sample(c(" he", "He"), size = 36, replace = TRUE))
+pronouns <- c(sample(c(" she", "She"), size = 720, replace = TRUE), 
+              sample(c(" he", "He"), size = 720, replace = TRUE))
 
-example_text <- example_words %>%
+example_text <- data_frame(word = example_words) %>%
     mutate(pronoun = pronouns,
-           phrase = str_c(pronoun, word, sep = " ")) %>%
-    pull(phrase) %>%
-    map_df(function(x) all_lines %>%
+           phrase = str_c(pronoun, word, sep = " "),
+           text = map_chr(phrase, function(x) all_lines %>%
                               filter(nchar(text) < 180,
@@
                               sample_n(1) %>%
-               select(text)) %>%
-    bind_cols(example_words) %>%
+                              pull(text))) %>%
     select(word, text)
@@
 
-```{r gender_ratio, echo = FALSE, dependson="pronoun_imdb", fig.width=8, fig.height=8}
+```{r gender_scatter, echo = FALSE, dependson="pronoun_imdb", fig.width=8, fig.height=8}
 library(viridis)
 
-she_gender_ratio <- pronoun_imdb %>%
-    inner_join(gender, by = "imdb") %>% ## to get gender of writers
-    filter(word1 == "she",
-           str_detect(word2, "[a-z]+"),
-           nchar(word2) > 2) %>%
+writer_counts <- pronoun_imdb %>%
+    inner_join(gender, by = "imdb") %>%
     group_by(word2) %>%
@@
     ungroup %>%    
-    count(gender, word2, total) %>%
-    spread(gender, n, fill = 0) %>%
-    mutate(female = (female + 1) / sum(female + 1),
-           male = (male + 1) / sum(male + 1),
-           she_ratio = female / male,
-           she_logratio = log2(she_ratio)) %>%
-    arrange(desc(she_logratio))
+    count(gender, word1, word2, total) %>%
+    unite(about, gender, word1) %>%
+    top_n(1600, total) %>%
+    spread(about, n, fill = 0)
 
-he_gender_ratio <- pronoun_imdb %>%
-    inner_join(gender, by = "imdb") %>% ## to get gender of writers, etc
-    filter(word1 == "he",
-           str_detect(word2, "[a-z]+"),
-           nchar(word2) > 2) %>%
-    group_by(word2) %>%
-    mutate(total = n_distinct(scriptID)) %>%
-    ungroup %>%
-    count(gender, word2, total) %>%
-    spread(gender, n, fill = 0) %>%
-    mutate(female = (female + 1) / sum(female + 1),
-           male = (male + 1) / sum(male + 1),
-           he_ratio = female / male,
-           he_logratio = log2(he_ratio)) %>%
-    arrange(desc(he_logratio))
-
-she_gender_ratio %>%
-    top_n(300, total) %>%
-    group_by(she_logratio < 0) %>%
-    top_n(15, abs(she_logratio)) %>%
-    ungroup() %>%
-    mutate(word = reorder(word2, she_logratio)) %>%
-    ggplot(aes(word, she_logratio, color = she_logratio < 0)) +
-    geom_segment(aes(x = word, xend = word,
-                     y = 0, yend = she_logratio), 
-                 size = 1.1, alpha = 0.6) +
-    geom_point(size = 3.5) +
-    coord_flip() +
-    labs(x = NULL, 
-         y = "Relative use by writers who are women compared to men",
-         title = "Words used for women characters by women and men writers in film set directions",
-         subtitle = "From ~2000 films, of the top 300 words") +
-    scale_color_discrete(name = "", labels = c("More from women", "More from men")) +
-    scale_y_continuous(breaks = seq(-3, 3),
-                       labels = c("0.125x", "0.25x", "0.5x", 
-                                  "Same", "2x", "4x", "8x"))
-
-```
-
-In our dataset, about 15% of film writers are women and about 85% are men.
-If women were more equitably represented in the ranks of Hollywood writers, our analysis indicates we would see fewer women in movies disappearing, reacting, and sobbing and more women loving, writing, and searching.
-And flinging things around, apparently!
-
-This plot shows one way to look at differences between writers who are men and women.
-Let's look a little deeper, though, to learn more.
-For example, do some of these differences hold true no matter what kind of character a woman is writing?
-What is the interaction between *writers* who are men and women and *characters* who are men and women?
-
-```{r gender_scatter, echo = FALSE, dependson="gender_ratio", fig.width=8, fig.height=8}
-writer_ratios <- she_gender_ratio %>%
-    select(word2, she_freq = she_ratio, she_logratio, she_total = total) %>%
-    left_join(he_gender_ratio %>%
-                  select(word2, he_freq = he_ratio, he_logratio, he_total = total)) %>%
-    top_n(300, she_total)
+writer_ratios <- writer_counts %>%
+    mutate_at(vars(female_he:male_she), funs((. + 1) / sum(. + 1))) %>%
+    mutate(female_ratio = female_she / female_he,
+           female_logratio = log2(female_ratio),
+           male_ratio = male_she / male_he,
+           male_logratio = log2(male_ratio)) %>%
+    arrange(desc(female_logratio))
 
@@
 writer_ratios %>%
-    ggplot(aes(she_logratio, he_logratio, label = word2,
-               size = (she_total + he_total),
-               color = she_freq / he_freq)) +
+    ggplot(aes(female_logratio, male_logratio, label = word2,
+               size = total,
+               color = female_ratio / male_ratio)) +
     annotate("text", x = 1.2, y = 1.2,
-             label = "Female writers\ndescribing men and women",
+             label = "All writers\ndescribing women",
              family = "RobotoCondensed-Regular") +
     annotate("text", x = -1.2, y = -1.2,
-             label = "Male writers\ndescribing men and women",
+             label = "All writers\ndescribing men",
              family = "RobotoCondensed-Regular") +
@@
 *Hover for word for all points*
+
+In our dataset, about 15% of film writers are women and about 85% are men.
+If women were more equitably represented in the ranks of Hollywood writers, our analysis indicates we would see fewer women in movies disappearing, reacting, and sobbing and more women loving, writing, and searching.
+And flinging things around, apparently!
+
+This plot shows one way to look at differences between writers who are men and women.
+Let's look a little deeper, though, to learn more.
+For example, do some of these differences hold true no matter what kind of character a woman is writing?
+What is the interaction between *writers* who are men and women and *characters* who are men and women?
 

### 2017-08-20 draft_post.Rmd
Update draft post
Update copy based on feedback

@@
 
-How are women portrayed in film? It's complicated; that question might make you think of a male protagonist's romantic interest, a damsel in distress who needs to be rescued, or maybe Wonder Woman.
+How are women portrayed in film? It’s complicated; that question might make you think of a male protagonist’s romantic interest, a damsel in distress who needs to be rescued, or Wonder Woman.
 
 One way to quantitatively measure how women are portrayed in film is to look at scene directions in film scripts.
-Scene directions are the part of a script that are not dialogue, describing what's happening on screen and telling actors how to move and how to deliver their lines.
-These scene directions communicate to the actors, producers, and director what story the script is working to tell.
+Scene directions are the part of a script that are not dialogue, describing what’s happening on screen and telling actors how to move and how to deliver their lines.
 
-In this analysis, we used text mining to identify words that are paired with the pronouns "he" and "she" in scene directions for over 2000 film scripts for movies released from the 1930s to today.
-We then analyzed which words are more likely to come after one compared to the other.
-Which words are most likely to be used with "she" in film script scene directions compared to those used with "he"?
+**In this analysis, we used text mining to identify words that are paired with the pronouns “he” and “she” in scene directions for about 2,000 film scripts for movies released from the 1930s to today.** We then analyzed which words are more likely to come after one or the other.
 
@@
 
-Now let's look at the top 800 words, including those that are used about evenly after "he" and "she".
+Now let’s look at the top 800 words, including those that are used about evenly after “he” and “she”.
 
@@
 
+Hollywood can be a tough place to work as a creative woman, either writing, directing, or producing films.
+We used our text mining approach to explore the impact that the gender of a writer has on how characters are portrayed.
+Using IMDB biographies, pictures, and names, we manually classified the genders of writers for our film script dataset.
+
+English has two singular third person pronouns most often used for people, “he” and “she”.
+In this analysis, for both the text data and the identification of gender for film writers, we have chosen to identify men and women with the pronouns “he” and “she”.
+Using this type of classification, anyone (writer or character) that uses the pronoun “she” would be classified as a woman.
+
+With these data, we can examine how male and female writers portray women in film.
+We can dig deeper into the kind of analysis we showed above and see how the results depend on who is writing a character.
+Do women writers portray women differently?
+What are the words that both male and female writers use about equally when crafting characters who are women, or men?
+What are the words that they use differently?
+How would the overall cultural representation of women be different if there were more women writing the movies we watch?
+For this part of the analysis, we will narrow the focus to the most commonly used 400 words.
+
 *Rough mockup for viz of writer viz*
-
-Hollywood can be a tough place to work as a creative woman, either writing, directing, or producing films.
-We can use our text mining approach to explore the impact that the gender of a writer has on how characters are portrayed.
-We used IMDB biographies, pictures, and names to manually classify the genders of writers for our film script dataset.
-
-Gender can be a complicated identification for people, but English has two singular third person pronouns most often used for people, "he" and "she".
-In this analysis, for both the text data and the identification of gender for film writers, we have chosen to identify men and women with the pronouns "he" and "she".
-Using this type of classification, a transgender woman (either a writer or a character in a script) described with the pronoun "she" would be classified as a woman.
-
-Using this connection to who wrote these scripts, we can examine how writers who are men and women are portraying women in film.
-Do women writers portray women differently?
-How would the overall cultural representation of women be different if there were more women writing the movies we watch?
 
@@
 
-In our dataset, about 15% of film writers are women and about 85% are men.
-If women were more equitably represented in the ranks of Hollywood writers, our analysis indicates we would see fewer women in movies disappearing, reacting, and sobbing and more women loving, writing, and searching.
-And flinging things around, apparently!
+In our dataset, about 15% of film writers were women and about 85% were men.
+If women were more equitably represented in the ranks of Hollywood writers, our analysis indicates we would see fewer female characters responding, kissing, and crying and more women spying, writing, and finding things.
 
-This plot shows one way to look at differences between writers who are men and women.
-Let's look a little deeper, though, to learn more.
-For example, do some of these differences hold true no matter what kind of character a woman is writing?
-What is the interaction between *writers* who are men and women and *characters* who are men and women?
+There are some words that both male and female writers are likely to use when directing a character of a certain gender..
+We see that women in film are more likely, compared to male characters, to gasp, hurry, smile, hesitate, and stir (mostly while cooking), regardless of whether the writer is a man or a woman.
+Men in film are more likely, compared to women, to smash things, draw their weapons, grin, wink, point, talk *and* speak, when being written by both male and female screenwriters.
 
-The size of the circle in this plot shows how often that word is used overall in film scripts; a word like "smiles" is used more often and a word like "understands" is used less often.
-Words close to an axis are used about the same with "he" and "she" for that kind of writer, and words far away from an axis exhibit more dramatic differences.
+We can also see remarkable differences in how male and female writers portray characters who are men and women.
+When describing the opposite gender, both men and women use some overtly romantic and sexual words like “kiss”, and “stroke”, as well as more subtle words like “respond” and “embrace”.
+When writing for the opposite gender, writers also use words that imply, well, less happy outcomes, such as “cry”, “glare”, and “died”.
 
-There are some words that writers who are men and women are more likely to use, no matter what kind of character they are writing.
-In the upper right quadrant, we find the words that writers who are women are more likely to use.
-Writers who are women are more likely to write characters who sing, love, shift, sink into things, and burst out or into places.
-And lots of flinging!
-The lower left quadrant shows the words that writers who are men are more likely to use, for both male and female characters.
-Writers who are men are more likely to write characters who react, clutch, dive, shout, duck, and emerge from places.
+When characters are penned by an author of their same gender, they are more likely to wince, jerk, fumble, and perhaps most remarkably, write on screen.
+There are verbs here that are active but less explicitly testosterone-fueled than when writers create male characters; when writers create characters the same gender as themselves, these characters spy, scan, sprint, and climb.
+These characters also search, remember, and realize.
+A woman in a movie doing such things is a far cry from the giggling, squealing, blushing character we met at the beginning of this essay.
 
-In the other quadrants, we can see remarkable differences in how writers who are men and women portray characters who are men and women.
-If you look in the upper left quadrant, we find words that writers use in describing characters of the opposite gender.
-There are some romantic and sexual words here, like "kiss", "gaze", and "stroke", as well as words that imply, well, less happy outcomes, such as "disappears" and "died".
-The lower right quadrant shows us the words that writers use to portray characters the same gender as them.
-These characters wince, jerk, fumble, and perhaps most remarkably, write on screen.
-There are verbs here that are active but less explicitly testosterone-fueled than the lower left quadrant; writers of the same gender create characters who crawl, climb, play, and scan.
-These characters also hear and understand.
-A woman in a movie doing such things is a far cry from the giggling, squealing, blushing character we met at the beginning of this essay.
+> The code used in analysis is [publicly available on GitHub](https://github.com/juliasilge/women-in-film).
+The data set for this analysis included 1,966 scripts for films released between 1929 and 2015; most are from 1990 and after.
+Each script was processed to extract only the set directions, excluding dialogue from this analysis.
+We then identified all [bigrams in these scripts that had either “he” or “she” as the first word in the bigram](https://juliasilge.com/blog/gender-pronouns).
+Then, we calculated a log odds ratio to find words that exhibit the biggest differences between relative use for “she” and “he”.
+We removed stop words and did some other minimal text cleaning to maintain meaningful results.
+We calculated the overall log odds ratio for the 800 most commonly used words, and then log odds ratios for only scripts with male writers and female writers for the 400 most commonly used words.
+Scripts often have more than one writer and could be counted in both categories.
+To learn more about text mining analyses like this one and how to perform them, [check out Julia’s book](http://tidytextmining.com).
 

### 2017-08-22 draft_post.Rmd
Some edits, based on feedback from copy editor

@@
 
-How are women portrayed in film? It’s complicated; that question might make you think of a male protagonist’s romantic interest, a damsel in distress who needs to be rescued, or Wonder Woman.
+In April 2016, we [broke down](https://pudding.cool/2017/03/film-dialogue/) film dialogue by gender.
+The essay presented an imbalance in which men delivered more lines than women across 2,000 screenplays.
+But quantity of lines is only part of the story.
+What characters do matters, too.
 
-One way to quantitatively measure how women are portrayed in film is to look at scene directions in film scripts.
-Scene directions are the part of a script that are not dialogue, describing what’s happening on screen and telling actors how to move and how to deliver their lines.
+Gender tropes (e.g., [women are pretty/men act, men don’t cry](http://tvtropes.org/pmwiki/pmwiki.php/Main/MenAreStrongWomenArePretty)) are just as important as dialogue in understanding how men and women are portrayed on-screen.
+These stereotypes result from many components, including casting, acting, directing, etc.
 
-**In this analysis, we used text mining to identify words that are paired with the pronouns “he” and “she” in scene directions for about 2,000 film scripts for movies released from the 1930s to today.** We then analyzed which words are more likely to come after one or the other.
+The film script, arguably, is ground zero—the source material by which everyone is influenced.
+And in film scripts, there’s dialogue and screen direction.
+For example, let’s take this iconic scene from Titanic:
+
+> compare dialogue/set directions here
+
+The curious data here is less what Rose says (“I’m flying”) and more what the screen direction prescribes (“she smiles dreamily,” “he pushes against her”).
+In the following analysis, we go deep on screen direction to understand gender tropes.
+**We examined 2,000 scripts and broke down every screen direction mapped to the pronouns “he” and “she.”**
 
@@
 
-There are dramatic differences in the kinds of words we see here.
-In movies, women are more likely to snuggle, giggle, squeal, and sob while men are more likely to strap things on, gallop, shoot, howl, and kill.
-We see evidence here of the tropes and storytelling conventions that propel so many films, and how men, women, and their relationships are often portrayed.
+These are the most extreme examples.
+There is a high likelihood that women will snuggle, giggle, squeal, and sob, relative to men.
+Conversely, men are more likely to strap, gallop, shoot, howl, and kill.
 
-Now let’s look at the top 800 words, including those that are used about evenly after “he” and “she”.
+Let’s now examine the 800 most commonly used pronoun pairs in screen direction.
 
@@
 
-Hollywood can be a tough place to work as a creative woman, either writing, directing, or producing films.
-We used our text mining approach to explore the impact that the gender of a writer has on how characters are portrayed.
-Using IMDB biographies, pictures, and names, we manually classified the genders of writers for our film script dataset.
-
-English has two singular third person pronouns most often used for people, “he” and “she”.
-In this analysis, for both the text data and the identification of gender for film writers, we have chosen to identify men and women with the pronouns “he” and “she”.
-Using this type of classification, anyone (writer or character) that uses the pronoun “she” would be classified as a woman.
-
-With these data, we can examine how male and female writers portray women in film.
-We can dig deeper into the kind of analysis we showed above and see how the results depend on who is writing a character.
-Do women writers portray women differently?
-What are the words that both male and female writers use about equally when crafting characters who are women, or men?
-What are the words that they use differently?
-How would the overall cultural representation of women be different if there were more women writing the movies we watch?
-For this part of the analysis, we will narrow the focus to the most commonly used 400 words.
+Next, let’s examine how the writer’s gender affects characters’ behavior.
+Do women writers use different language for women roles?
+What are the words that both male and female writers use about equally when describing characters?
+Would results change dramatically if there were more women writers?
+First, we will narrow the data set to the most commonly used 400 words.
 
@@
 
-In our dataset, about 15% of film writers were women and about 85% were men.
-If women were more equitably represented in the ranks of Hollywood writers, our analysis indicates we would see fewer female characters responding, kissing, and crying and more women spying, writing, and finding things.
+There are some directions where the writer’s gender makes no difference.
+Relative to men, women gasp, hurry, smile, hesitate, and stir (mostly while cooking), regardless of whether the writer is a man or a woman.
+Men are consistently more likely to smash things, draw their weapons, grin, wink, point, talk, and speak.
 
-There are some words that both male and female writers are likely to use when directing a character of a certain gender..
-We see that women in film are more likely, compared to male characters, to gasp, hurry, smile, hesitate, and stir (mostly while cooking), regardless of whether the writer is a man or a woman.
-Men in film are more likely, compared to women, to smash things, draw their weapons, grin, wink, point, talk *and* speak, when being written by both male and female screenwriters.
+When describing the opposite gender, both men and women use some overtly romantic and sexual words, such as “kiss” and “stroke,” as well as more subtle words including “respond” and “embrace.”
 
-We can also see remarkable differences in how male and female writers portray characters who are men and women.
-When describing the opposite gender, both men and women use some overtly romantic and sexual words like “kiss”, and “stroke”, as well as more subtle words like “respond” and “embrace”.
-When writing for the opposite gender, writers also use words that imply, well, less happy outcomes, such as “cry”, “glare”, and “died”.
-
-When characters are penned by an author of their same gender, they are more likely to wince, jerk, fumble, and perhaps most remarkably, write on screen.
-There are verbs here that are active but less explicitly testosterone-fueled than when writers create male characters; when writers create characters the same gender as themselves, these characters spy, scan, sprint, and climb.
-These characters also search, remember, and realize.
-A woman in a movie doing such things is a far cry from the giggling, squealing, blushing character we met at the beginning of this essay.
+But there are differences.
+In our data set, 15% of film writers were women; 85% were men.
+Should Hollywood reach gender parity, we’d expect fewer women characters to respond, kiss, and cry.
+The increase in female writers would also mean women would be more likely to spy, find things, and, perhaps most remarkably, write on-screen.
 
@@
 We then identified all [bigrams in these scripts that had either “he” or “she” as the first word in the bigram](https://juliasilge.com/blog/gender-pronouns).
-Then, we calculated a log odds ratio to find words that exhibit the biggest differences between relative use for “she” and “he”.
+
+> Then, we calculated a log odds ratio to find words that exhibit the biggest differences between relative use for “she” and “he”.
 We removed stop words and did some other minimal text cleaning to maintain meaningful results.
@@
 To learn more about text mining analyses like this one and how to perform them, [check out Julia’s book](http://tidytextmining.com).
+
+> Writers’ gender was determined via IMDB biographies, pictures, and names.
+
+> English has two singular third-person pronouns most often used for people, “he” and “she.” In this analysis, for both the text data and the identification of gender for film writers, we have chosen to identify men and women with the pronouns “he” and “she.” Using this type of classification, any writer or character associated with the pronoun “she” is classified as a woman.
 
